Automatic Matching of Bullet Lands

### 2016-01-14 imaging-paper.Rnw
Fix broken supplement reference

\begin{figure}[hbtp]
  \centering
\begin{subfigure}[t]{.54\textwidth}\centering
\caption{View from the side.\label{fig:sidex3p}}{%
      \includegraphics[width=\textwidth]{images/sidex3p.png}
    }
\end{subfigure}    
\begin{subfigure}[t]{.45\textwidth}\centering
    \caption{View from the top.\label{fig:topx3p}}{%
    \includegraphics[width=\textwidth]{images/topx3p.png}
    }
\end{subfigure}
\caption{An example of a scan of a bullet land from one groove to the next. }
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". For notational simplicity, we refer to a particular land of some bullet as bullet X-Y, where X is the bullet identifier, and Y is the land number. An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}. These figures show side and top profiles of the land respectively. The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artifact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clockwise or counter-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic, i.e.\ a feature that pertains to a particular class of firearms, and is not unique at the individual barrel/bullet level.

@@

In an approach to analyze the striation pattern we extract a \emph{bullet profile} \citep{ma:2004} by taking a cross section across the surface measurements for a fixed value of $x$.
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in supplement section~\ref{supp:circular}.
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

>>>>

\begin{figure}[hbtp]
  \centering
\begin{subfigure}[t]{.54\textwidth}\centering
\caption{View from the side.\label{fig:sidex3p}}{%
      \includegraphics[width=\textwidth]{images/sidex3p.png}
    }
\end{subfigure}    
\begin{subfigure}[t]{.45\textwidth}\centering
    \caption{View from the top.\label{fig:topx3p}}{%
    \includegraphics[width=\textwidth]{images/topx3p.png}
    }
\end{subfigure}
\caption{An example of a scan of a bullet land from one groove to the next. }
\end{figure}
Each fired bullet is provided in the form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". For notational simplicity, we refer to a particular land of some bullet as bullet X-Y, where X is the bullet identifier, and Y is the land number. An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}. These figures show side and top profiles of the land respectively. The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artifact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clockwise or counter-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic, i.e.\ a feature that pertains to a particular class of firearms, and is not unique at the individual barrel/bullet level.

@@

In an approach to analyze the striation pattern we extract a \emph{bullet profile} \citep{ma:2004} by taking a cross section across the surface measurements at a fixed value of the bullet's height, denoted by $x$.
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in Supplement section~\ref{supp:cylindrical}.
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.
